Reliably estimating the impact of a new control strategy in a building

### 2024-09-08 code/manuscript.Rmd
Updated manuscript structure

output:
  bookdown::word_document2:
    reference_docx: "../paper/template.docx"
editor_options: 
  markdown: 
    wrap: 72
# bibliography: references.bib
# biblio-style: apalike

@@

# knitr setup
knitr::opts_chunk$set(echo = F, 
                      message = F,
                      warning = F,
                      dev = "jpeg",
                      cache = T,
                      dpi = 300,
                      fig.path = "figs",
                      fig.show = "hold",
                      fig.pos = "b", 
                      fig.path = "../figs/results/manuscript")

@@

```{r libraries, include = FALSE, cache = FALSE}

>>>>

output:
  bookdown::word_document2:
    reference_docx: "../paper/TF_Template_Word_Mac_2011.dotx"
editor_options: 
  markdown: 
    wrap: 72
# bibliography: references.bib
# biblio-style: apalike

@@

# knitr setup
knitr::opts_chunk$set(echo = F, 
                      message = F,
                      warning = F,
                      dev = "jpeg",
                      # cache = T,
                      dpi = 300,
                      fig.path = "figs",
                      fig.show = "hold",
                      fig.pos = "b", 
                      fig.path = "../figs/manuscript")

@@

```{r prep, include = FALSE, cache = FALSE}
#### LIBRARIES ####
require(pacman)

# load packages using pacman
pacman::p_load(tidyverse, lubridate, here) #effect size

# turn off scientific notation
options(scipen = 999, digits = 15)

# set directory
here::i_am("manuscript.rmd")

# set default theme for ggplot
theme_set(theme_minimal())

# define base ggplot theme
theme_update(plot.title = element_text(size = 14, colour = "grey20", face = "bold", hjust = 0.5),
             plot.subtitle = element_text(size = 10, colour = "grey20", face = "italic", hjust = 0.5, margin = margin(b = 10)),
             plot.caption = element_text(size = 10, colour = "grey20", face = "italic", hjust = 0.5),
             plot.background = element_rect(fill = "white", colour = NA),
             panel.grid.minor = element_blank(),
             panel.grid.major = element_blank(),
             axis.text = element_text(size = 10),
             strip.text = element_text(size = 10, color = "grey20", face = "bold"),
             strip.background = element_blank())

ls_colors <- c("Baseline" = "#99d8c9",
               "Measured baseline" = "#99d8c9",
               "Adjusted baseline" = "#99d8c9",
               "Projected baseline\n(no change)" = "#1b9e77",
               "Intervention" = "#fdbb84",
               "Measured interv" = "#fdbb84",
               "True savings" = "black",
               "True normalized savings" = "black")

#### FUNCTIONS ####
# Function defined to read downloaded tmy files
get_tmy <- function(all_sites, readfile_path){

  df_tmy <- data.frame()

  for (site in all_sites){
    df <- read_csv(paste0(readfile_path, "tmy/", str_glue("{site}.epw")),
                   skip = 8, col_types = "ddddd-d---------------------------------",
                   col_names = c("year", "month", "day", "hour", "min", "tmy")) %>%
      mutate(year = 2017,
             time = ymd_h(paste(paste(year, month, day, sep = "-"), hour, sep = " ")),
             temp = tmy) %>%
      dplyr::select(time, temp) %>% 
      mutate(site = site)

    df_tmy <- rbind(df_tmy, df)
  }

  return(df_tmy)
}

# define parameters
sprt_param <- list(baseline = "Baseline",
                   strategy = "Intervention",
                   parameter = "power_ave",
                   label = "power",
                   n_weeks = 48)

block_params <- list(start_date = "2016-01-01",
                     n_weeks = 108,
                     n_seasons = 9, 
                     block_unit = 12)
```

```{r readdata, include=FALSE}

#### READ DATA ####
# Tidy dataset
readfile_tidy <- str_glue("../readfiles/tidy/")

df_energy_tidy <- read_rds(paste0(readfile_tidy, "df_energy.rds"))
df_meta_tidy <- read_rds(paste0(readfile_tidy, "df_meta.rds"))
df_weather_tidy <- read_rds(paste0(readfile_tidy, "df_weather.rds"))
df_sprt_all_tidy <- read_rds(paste0(readfile_tidy, "df_sprt_all.rds"))
df_seq_FS_tidy <- read_rds(paste0(readfile_tidy, "df_seq_FS.rds"))
df_NRE_occ <- read_rds(paste0(readfile_tidy, "df_NRE_occ.rds"))
df_MD_tidy <- read_rds(paste0(readfile_tidy, "df_MD.rds"))
df_FS_tidy <- read_rds(paste0(readfile_tidy, "df_FS.rds"))
df_eui_tidy <- read_rds(paste0(readfile_tidy, "df_eui.rds"))
df_cont_MD_tidy <- read_rds(paste0(readfile_tidy, "df_cont_MD.rds"))
df_cont_FS_tidy <- read_rds(paste0(readfile_tidy, "df_cont_FS.rds"))

all_sites_tidy <- df_energy_tidy %>%
  select(site) %>%
  distinct() %>%
  arrange(site)

all_types_tidy <- df_energy_tidy %>%
  select(type) %>%
  mutate(type = as.factor(type)) %>%
  distinct()

all_names_tidy <- df_energy_tidy %>%
  select(name) %>%
  distinct(name)

# Messy dataset
readfile_messy <- str_glue("../readfiles/messy/")

df_energy_messy <- read_rds(paste0(readfile_messy, "df_energy.rds"))
df_meta_messy <- read_rds(paste0(readfile_messy, "df_meta.rds"))
df_weather_messy <- read_rds(paste0(readfile_messy, "df_weather.rds"))
df_sprt_all_messy <- read_rds(paste0(readfile_messy, "df_sprt_all.rds"))
df_seq_FS_messy <- read_rds(paste0(readfile_messy, "df_seq_FS.rds"))
df_MD_messy <- read_rds(paste0(readfile_messy, "df_MD.rds"))
df_FS_messy <- read_rds(paste0(readfile_messy, "df_FS.rds"))
df_eui_messy <- read_rds(paste0(readfile_messy, "df_eui.rds"))
df_cont_MD_messy <- read_rds(paste0(readfile_messy, "df_cont_MD.rds"))
df_cont_FS_messy <- read_rds(paste0(readfile_messy, "df_cont_FS.rds"))
df_FS_nsprt <- read_rds(paste0(readfile_messy, "df_FS_nsprt.rds"))
df_MD_nsprt <- read_rds(paste0(readfile_messy, "df_MD_nsprt.rds"))
df_seq_FS_nsprt <- read_rds(paste0(readfile_messy, "df_seq_FS_nsprt.rds"))

all_sites_messy <- df_energy_messy %>%
  select(site) %>%
  distinct() %>%
  arrange(site)

all_types <- df_energy_messy %>%
  select(type) %>%
  mutate(type = as.factor(type)) %>%
  distinct()

all_names <- df_energy_messy %>%
  select(name) %>%
  distinct(name)
```

# Introduction

## Background

### Conventional M&V

### Randomized (rapid) M&V

### Non-routine events

## Literature review

## Objectives

The objectives of this paper include:

1.  Demonstrate the implementation of the proposed randomized rapid M&V
    method using a public available dataset. We ensured the
    reproducibility of the M&V method by making the analysis code open
    source including randomized schedule generation, sequential
    statistical analysis, energy modeling and normalized saving
    calculation. Using the available open resources, building analysts
    should be able to seamlessly integrate and apply them in their own
    M&V projects.

2.  Compare the energy saving estimation accuracy between the
    conventional and the randomized method. In particular, this study
    extends the comparison to large samples of buildings of various
    types and across multiple climate zones.

3.  Verify the superior robustness of the randomized method over the
    conventional method. By using the realistic measurements from
    real-world buildings, which contains various sources of noises,
    could largely reflect the challenges that a building analyst would
    be facing in any real project. Particularly, as we will demonstrate
    in the following sections, non-routine events (i.e. 'noises' in the
    measurements) have less impact in the energy saving estimation when
    the analyst uses the randomized approach.

# Method

As mentioned, this study leverages a large public dataset to demonstrate
the energy saving estimation results of a novel M&V method inspired by
other scientific research fields. We outlined the methodology of the
study in figure and outlined several key steps in this section.

```{r flowchart}

## Data filtering process

### 'Tidy' dataset - buildings with the same two-year electricity usage

### 'Messy' dataset - buildings with reasonable change

## Control intervention - chilled water supply temperature reset

## Building Energy modeling

# Results

## Randomized M&V results

### Saving estimation accuracy comparison ('tidy' dataset results)

### Required estimation time

### Continue sampling results

## Influence of non-routine events

### Example non-routine event: occupancy change

### Saving estimation accuracy comparison ('messy' dataset results)

# Discussion

# Conclusion
